---
title: "Book Sales 2019"
author: "Amelia Rudberg"
date: "2023-01-13"
output: html_document
---

### Prepping the Data 
***Start by loading the tidyverse package***
```{r, message=FALSE}
library(tidyverse)
```

***Then, load the CSV***
```{r}
sales2019<-read_csv("sales2019.csv")
```
***Next, describe the column names and types***
```{r}
col_names<-colnames(sales2019)
col_names
for(c in col_names){
  print("Column Name:")
  print(c)
  print("Column Type:")
  print(typeof(sales2019[[c]]))
  print("")
}
for(c in col_names){
  print("Column Name:")
  print(c)
  print("Unique Values:")
  print(unique(sales2019[[c]]))
  print("-----")
}
```

The columns are: Date (character), user_submitted_review (character), title (character), total_purchased (double), and customer_type (character). 
The columns with missing values are: user_submitted_review and total_purchased.   

### Cleaning the Data 

*** First we will remove any rows with missing data in "user_submitted_review". 
```{r}
sales2019<- sales2019 %>% filter(!is.na(sales2019[["user_submitted_review"]]))
dim(sales2019)
5000-4115
```
885 rows were removed due to missing reviews. 

***Next we will replace any missing data in total_purchased with an average of the column***
```{r}
average_purchase<- sales2019 %>% filter(!is.na(sales2019[["total_purchased"]])) %>% pull(total_purchased) %>% mean
average_purchase
```

The average purchase is 3.99, so we will use that for any missing values, rounded up to 4.  

```{r}
sales2019<- sales2019 %>% mutate(
  new_total_purchased = if_else(is.na(total_purchased), 4, total_purchased)
)
```

### Processing Review Data 
***First we will look at the unique reviews***
```{r}
unique(sales2019[["user_submitted_review"]])
```
The positive reviews contain "Never", "Awesome", and "learned". 

```{r}
is_positive_function<- function(review) {
  review_positive = case_when(
    str_detect(review, "Awesome") ~ TRUE, 
    str_detect(review, "Never") ~ TRUE, 
    str_detect(review, "learned") ~ TRUE, 
    TRUE ~ FALSE
  )
}
sales2019<- sales2019 %>% 
  mutate(
  is_positive2 = unlist(map(user_submitted_review, is_positive_function))
)
```

### Comparing Pre/Post Program Data

***First, convert the date to the proper format, and add a pre/post column***

```{r}
sales2019<- sales2019 %>% mutate(
  date_status= if_else(mdy(date) < ymd("2019-07-01"), "PRE", "POST"
)
)
```

***The create a summary table***

```{r}
pre_post_summary<- sales2019 %>% group_by(date_status) %>% summarize(
  books_purchased = sum(new_total_purchased)
)
pre_post_summary

```
We can see from the newly created summary table that the program did not increase sales.

Next we can look at if certain titles increased sales more. 
```{r}
sales2019 %>% group_by(date_status, title) %>% summarize(
  books_purchased = sum(new_total_purchased)
) %>%
arrange(title, date_status)
```
Next we can compare by customer type.  
```{r}
pre_post_summary_customer<- sales2019 %>% group_by(date_status, customer_type) %>% summarize(
  books_purchased = sum(new_total_purchased)
) %>%
  arrange(customer_type, date_status)
pre_post_summary_customer
```
Through this analysis we can see that sales incrased within the Business customer type, but decreased in the Individual customer type.   

Now we will compare review sentiment pre and post program.
```{r}
pre_post_summary_review<- sales2019 %>% group_by(date_status, is_positive2) %>% summarize(
  books_purchased = sum(new_total_purchased)
) %>% arrange(is_positive2, date_status)
pre_post_summary_review
```
After the program there were more positive reviews and fewer negative reviews. 
