---
title: "Book Sales 2019"
author: "Amelia Rudberg"
date: "2023-01-13"
output: html_document
---

### Prepping the Data 
***Start by loading the tidyverse package***
```{r, message=FALSE}
library(tidyverse)
```

***Then, load the CSV***
```{r}
sales2019<-read_csv("sales2019.csv")
```
***Next, describe the column names and types***
```{r}
col_names<-colnames(sales2019)
col_names
for(c in col_names){
  print("Column Name:")
  print(c)
  print("Column Type:")
  print(typeof(sales2019[[c]]))
  print("")
}
for(c in col_names){
  print("Column Name:")
  print(c)
  print("Unique Values:")
  print(unique(sales2019[[c]]))
  print("-----")
}
```

The columns are: Date (character), user_submitted_review (character), title (character), total_purchased (double), and customer_type (character). 
The columns with missing values are: user_submitted_review and total_purchased.   

### Cleaning the Data 

*** First we will remove any rows with missing data in "user_submitted_review". 
```{r}
sales2019<- sales2019 %>% filter(!is.na(sales2019[["user_submitted_review"]]))
dim(sales2019)
5000-4115
```
885 rows were removed due to missing reviews. 

***Next we will replace any missing data in total_purchased with an average of the column***
```{r}
average_purchase<- sales2019 %>% filter(!is.na(sales2019[["total_purchased"]])) %>% pull(total_purchased) %>% mean
average_purchase
```

The average purchase is 3.99, so we will use that for any missing values, rounded up to 4.  

```{r}
sales2019<- sales2019 %>% mutate(
  new_total_purchased = if_else(is.na(total_purchased), 4, total_purchased)
)
```

